Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference with crowdsourcing?

### 2019-12-19 survey/survey.Rmd
aims clarified

## Aims

@@

2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
using a hexagon tile map display?
3. Do people find hexagon tile maps more difficult to read than choropleth maps?
4. Are the reasons for choosing a plot different depending on the type of display?
5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?

## Methodology

@@

## The variables being manipulated and measured?

>>>>

@@

2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when
using a hexagon tile map display?

additional considerations
 Do people find hexagon tile maps more difficult to read than choropleth maps?
 Are the reasons for choosing a plot different depending on the type of display?

## Experimental design

@@

## The variables being manipulated and measured
